---
title: "Journal (reproducible report)"
author: "Lukas Schwarz"
date: "2020-11-18"
output:
  html_document:
    pandoc_args: ["+RTS", "-M1024M", "-RTS"]
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Challenge: Intro to the tidyverse

Last compiled: `r Sys.Date()`

## Script
```{r plot1, fig.width=10, fig.height=7}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library("tidyverse")
library("readxl")
library("lubridate")
# 2.0 Importing Files ----
bikes <- read_xlsx("DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
order_lines <- read_xlsx("DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops <- read_xlsx("DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
# 3.0 Examining Data ----
# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- order_lines %>%
  left_join(bikes, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops, by = c("customer.id" = "bikeshop.id"))

# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  select(order.id, order.date, customer.id, product.id, quantity, price, name, location) %>%
  mutate(total_price = price * quantity) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_")) %>%
  separate(col = location,
           into = c("city", "state"),
           sep = ", ")

# 6.0 Business Insights ----
# 6.1 Sales by state ----
# Step 1 - Manipulate
bike_orders_state <- bike_orderlines_wrangled_tbl %>%
  transmute(total_price,state) %>%
  group_by(state) %>%
  summarise(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
# Step 2 - Visualize
bike_orders_state %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    x = "", # Override defaults for x and y
    y = "Revenue"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# 6.2 Sales by Year and Category 2 ----
# Step 1 - Manipulate
bike_orders_state_year <- bike_orderlines_wrangled_tbl %>%
  transmute(year = year(order_date),total_price,state) %>%
  group_by(state,year) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
# Step 2 - Visualize
bike_orders_state_year %>%
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    #subtitle = "Each product category has an upward trend",
    fill = "state" # Changes the legend name
  )

```

# Data Acquisition

Last compiled: `r Sys.Date()`

## API

```{r API}
library(tidyverse)
library(httr)
library(jsonlite)

resp <- GET("https://pokeapi.co/api/v2/type/15")
list =  resp %>%
  .$content %>%
  rawToChar() %>%
  fromJSON()
ice_pokemon <- list[["pokemon"]] 
ice_pokemon %>% head(n = 10)
```

## Web Scraping

```{r data acquisition}
library(tidyverse)
library(rvest)
library(stringr)
library(jsonlite)
library(glue)

home_url <- "https://www.radon-bikes.de"

html_home         <- read_html(home_url)

bike_category_tbl <- html_home %>%
  
  html_nodes(css = ".megamenu__item > a") %>%
  html_attr("href") %>%
  discard(.p = ~stringr::str_detect(.x,"wear|RADON LIFE|SERVICE & SUPPORT|DE")) %>%
  enframe(name = "position", value = "subdirectory") %>%
  mutate(url = glue("{home_url}{subdirectory}bikegrid/"))

get_bike_data <- function(url) {
  html_bike_category <- read_html(url)
  
  bike_url_tbl  <- html_bike_category %>%
    html_nodes(css = ".m-bikegrid__info > a") %>%
    html_attr("href") %>%
    enframe(name = "position", value = "url")
  
  bike_name_tbl <- html_bike_category %>%
    html_nodes(css =".a-heading--small") %>%
    html_text() %>%
    str_trim() %>%
    enframe(name = "position", value = "Model Name")
  
  bike_price_tbl <- html_bike_category %>%
    html_nodes(css =".m-bikegrid__price.currency_eur") %>%
    html_nodes(css = ".m-bikegrid__price--active") %>%
    html_text() %>%
    str_extract(pattern = "[0-9]+") %>% 
    as.numeric()%>%
    enframe(name = "position", value = "price euro") %>%
    left_join(bike_name_tbl) %>%
    left_join(bike_url_tbl)
}

bike_category_url_vec <- bike_category_tbl %>% 
  pull(url)

bike_data_lst <- map(bike_category_url_vec, get_bike_data)

bike_data_tbl_all <- bind_rows(bike_data_lst)
bike_data_tbl_all %>% head(n = 10)
```

# Data Wrangling

```{r Datawrangling, eval= FALSE}
library(tidyverse)
library(data.table)
library(vroom)

col_types <- list(
  id = col_character(),
  type = col_skip(),
  number = col_character(),
  country = col_skip(),
  date = col_date("%Y-%m-%d"),
  abstract = col_skip(),
  title = col_skip(),
  kind = col_skip(),
  num_claims = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip()
)

patent_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/patent.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)
setDT(patent_tbl)

col_types_assignee <- list(
  id = col_character(),
  type = col_character(),
  name_first = col_skip(),
  name_last = col_skip(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types_assignee,
  na         = c("", "NA", "NULL")
)

setDT(assignee_tbl)

col_types_patent_assignee <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip()
)

patent_assignee_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types_patent_assignee,
  na         = c("", "NA", "NULL")
)
setDT(patent_assignee_tbl)

col_types_uspc <- list(
  uuid = col_skip(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_skip(),
  sequence = col_skip()
)

uspc_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/uspc.tsv", 
  delim      = "\t", 
  col_types  = col_types_uspc,
  na         = c("", "NA", "NULL")
)
setDT(uspc_tbl)

#Question 1
setnames(assignee_tbl, "id", "assignee_id")

pat_ass_merged <- merge(x = patent_assignee_tbl , y = assignee_tbl , 
                        by    = "assignee_id")

patents_corporations <- pat_ass_merged[!is.na(organization) & type == 2, .N, by = organization][order(-N)]
patents_corporations  %>% head(10)

#Question 2
patent_tbl[,year := lubridate::year(date)]
patent_tbl_clean <- patent_tbl[, .(patent_id = id,year)]

table2 <- merge(x = pat_ass_merged , y = patent_tbl_clean , by = "patent_id")

patents_2019 <- table2[!is.na(organization) & year == 2019 & type == 2, .N, by = organization][order(-N)]
patents_2019 %>% head(10)

#Question 3
table3 <- merge(x = pat_ass_merged , y = uspc_tbl , by = "patent_id") %>%
  unique()

patents_per_corp <- pat_ass_merged[!is.na(organization), .N, by = organization][order(-N)] 

table3_expanded <- merge(x = table3 , y = patents_per_corp , by = "organization")

min_patents <- patents_per_corp[10, N]

sector <- table3_expanded[N >= min_patents, .N , by = mainclass_id][order(-N)]
sector %>% head(5)

```
```{r Result}
library(readr)
library(data.table)
Question1 <- read_rds("DS_101/02_data_wrangling/Q1")
Question1
Question2 <- read_rds("DS_101/02_data_wrangling/Q2")
Question2
Question3 <- read_rds("DS_101/02_data_wrangling/Q3")
Question3
```
# Data Visualization
## Challenge 1
```{r vis Ch1}
library(tidyverse)
library(lubridate)
library(scales)
library(ggrepel)

covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv") %>%
  filter(year == 2020 &countriesAndTerritories %in% c("Spain", "France", "Germany", "United_Kingdom", "United_States_of_America")) %>%
  mutate(date = make_date(year, month, day)) %>%
  mutate(month = month(date)) %>%
  arrange(countriesAndTerritories, date) %>%
  group_by(countriesAndTerritories) %>%
  mutate(cum_cases = cumsum(cases)) %>%
  ungroup()

max_table <- covid_data_tbl %>%
  filter(countriesAndTerritories == "United_States_of_America") %>%
  slice_max(cum_cases)

covid_data_tbl %>%
  
  ggplot(aes( x = date, y = cum_cases, color = countriesAndTerritories)) +
  
  geom_line(size = 1, linetype = 1) + 
  
  scale_y_continuous(breaks = c(0,2.5e6,5e6,7.5e6,10e6, 12.5e6),
                     labels = scales::dollar_format(scale = 1e-6, 
                                                    prefix = "",
                                                    suffix = "M")) +
  
  scale_x_date(date_breaks = "1 month",
               date_labels = "%B") + 
  
  theme_grey() +
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(face = "bold"),
        legend.position = "bottom",
        legend.title = element_text(face = "bold", size = 10),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold")) +
  
  scale_color_discrete(name = "Country",
                       labels = c("France", "Germany", "Spain", "UK", "USA")) +
  
  guides(col = guide_legend(nrow = 2)) +
  
  labs(
    title = "COVID-19 confirmed cases worldwide",
    x = "Year 2020",
    y = "Cummulative Cases"
  ) +
  
  geom_label_repel(aes(x=date, y=cum_cases, label=cum_cases),
             data = max_table,
             hjust = 1.5,
             fill = "#F763E0",
             color= "white")
```

## Challenge 2
```{r vis Ch2}
library(tidyverse)
library(lubridate)
library(scales)
library(maps)
world <- map_data("world")
covid_data_csv <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")# %>%
  
covid_data_tbl <- covid_data_csv %>%
  group_by(countriesAndTerritories) %>%
  summarise(deaths = sum(deaths),
            population = mean(popData2019)) %>%
  ungroup() %>% 
  mutate(mort_rate = deaths / population) %>%
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
  ))


covid_world <-left_join(world, covid_data_tbl, by = c("region" = "countriesAndTerritories"))

covid_world %>%
  
  ggplot(aes(x = long, y = lat, fill = mort_rate)) +
  
  geom_map(aes(map_id = region, colour = "grey"), map = world) +
  
  scale_colour_manual(values=c('grey'),
                      guide = FALSE) +

  scale_fill_continuous(name = "Mortality Rate",
                        low = "#fc8d59", high = "#7f0000",
                        limits = c(0,0.0012),
                        breaks = c(0.00,0.0003,0.0006,0.0009,0.0012),
                        labels = c("0.00 %", "0.03 %", "0.06 %", "0.09 %", "0.12 %")) +
  
  theme(axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank()) +

  
  labs(
    title = "Confirmed COVID-19 deaths relative to the size of the population",
    subtitle = "More than 1.2 Million COVID-19 deaths worldwide",
    caption = "Date: 30/11/2020",
    x = "",
    y = ""
  )

```
