---
title: "Journal (reproducible report)"
author: "Lukas Schwarz"
date: "2020-11-18"
output:
  html_document:
    pandoc_args: ["+RTS", "-M1024M", "-RTS"]
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Challenge: Intro to the tidyverse

Last compiled: `r Sys.Date()`

## Script
```{r plot1, fig.width=10, fig.height=7}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library("tidyverse")
library("readxl")
library("lubridate")
# 2.0 Importing Files ----
bikes <- read_xlsx("DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
order_lines <- read_xlsx("DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops <- read_xlsx("DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
# 3.0 Examining Data ----
# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- order_lines %>%
  left_join(bikes, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops, by = c("customer.id" = "bikeshop.id"))

# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  select(order.id, order.date, customer.id, product.id, quantity, price, name, location) %>%
  mutate(total_price = price * quantity) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_")) %>%
  separate(col = location,
           into = c("city", "state"),
           sep = ", ")

# 6.0 Business Insights ----
# 6.1 Sales by state ----
# Step 1 - Manipulate
bike_orders_state <- bike_orderlines_wrangled_tbl %>%
  transmute(total_price,state) %>%
  group_by(state) %>%
  summarise(sales = sum(total_price)) %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
# Step 2 - Visualize
bike_orders_state %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    x = "", # Override defaults for x and y
    y = "Revenue"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# 6.2 Sales by Year and Category 2 ----
# Step 1 - Manipulate
bike_orders_state_year <- bike_orderlines_wrangled_tbl %>%
  transmute(year = year(order_date),total_price,state) %>%
  group_by(state,year) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
# Step 2 - Visualize
bike_orders_state_year %>%
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    #subtitle = "Each product category has an upward trend",
    fill = "state" # Changes the legend name
  )

```

# Data Acquisition

Last compiled: `r Sys.Date()`

## API

```{r API}
library(tidyverse)
library(httr)
library(jsonlite)

resp <- GET("https://pokeapi.co/api/v2/type/15")
list =  resp %>%
  .$content %>%
  rawToChar() %>%
  fromJSON()
ice_pokemon <- list[["pokemon"]] 
ice_pokemon %>% head(n = 10)
```

## Web Scraping

```{r data acquisition}
library(tidyverse)
library(rvest)
library(stringr)
library(jsonlite)
library(glue)

home_url <- "https://www.radon-bikes.de"

html_home         <- read_html(home_url)

bike_category_tbl <- html_home %>%
  
  html_nodes(css = ".megamenu__item > a") %>%
  html_attr("href") %>%
  discard(.p = ~stringr::str_detect(.x,"wear|RADON LIFE|SERVICE & SUPPORT|DE")) %>%
  enframe(name = "position", value = "subdirectory") %>%
  mutate(url = glue("{home_url}{subdirectory}bikegrid/"))

get_bike_data <- function(url) {
  html_bike_category <- read_html(url)
  
  bike_url_tbl  <- html_bike_category %>%
    html_nodes(css = ".m-bikegrid__info > a") %>%
    html_attr("href") %>%
    enframe(name = "position", value = "url")
  
  bike_name_tbl <- html_bike_category %>%
    html_nodes(css =".a-heading--small") %>%
    html_text() %>%
    str_trim() %>%
    enframe(name = "position", value = "Model Name")
  
  bike_price_tbl <- html_bike_category %>%
    html_nodes(css =".m-bikegrid__price.currency_eur") %>%
    html_nodes(css = ".m-bikegrid__price--active") %>%
    html_text() %>%
    str_extract(pattern = "[0-9]+") %>% 
    as.numeric()%>%
    enframe(name = "position", value = "price euro") %>%
    left_join(bike_name_tbl) %>%
    left_join(bike_url_tbl)
}

bike_category_url_vec <- bike_category_tbl %>% 
  pull(url)

bike_data_lst <- map(bike_category_url_vec, get_bike_data)

bike_data_tbl_all <- bind_rows(bike_data_lst)
bike_data_tbl_all %>% head(n = 10)
```

# Data Wrangling

```{r Datawrangling, eval= FALSE}
library(tidyverse)
library(data.table)
library(vroom)

col_types <- list(
  id = col_character(),
  type = col_skip(),
  number = col_character(),
  country = col_skip(),
  date = col_date("%Y-%m-%d"),
  abstract = col_skip(),
  title = col_skip(),
  kind = col_skip(),
  num_claims = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip()
)

patent_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/patent.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)
setDT(patent_tbl)

col_types_assignee <- list(
  id = col_character(),
  type = col_character(),
  name_first = col_skip(),
  name_last = col_skip(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types_assignee,
  na         = c("", "NA", "NULL")
)

setDT(assignee_tbl)

col_types_patent_assignee <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip()
)

patent_assignee_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types_patent_assignee,
  na         = c("", "NA", "NULL")
)
setDT(patent_assignee_tbl)

col_types_uspc <- list(
  uuid = col_skip(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_skip(),
  sequence = col_skip()
)

uspc_tbl <- vroom(
  file       = "DS_101/02_data_wrangling/uspc.tsv", 
  delim      = "\t", 
  col_types  = col_types_uspc,
  na         = c("", "NA", "NULL")
)
setDT(uspc_tbl)

#Question 1
setnames(assignee_tbl, "id", "assignee_id")

pat_ass_merged <- merge(x = patent_assignee_tbl , y = assignee_tbl , 
                        by    = "assignee_id")

patents_corporations <- pat_ass_merged[!is.na(organization) & type == 2, .N, by = organization][order(-N)]
patents_corporations  %>% head(10)

#Question 2
patent_tbl[,year := lubridate::year(date)]
patent_tbl_clean <- patent_tbl[, .(patent_id = id,year)]

table2 <- merge(x = pat_ass_merged , y = patent_tbl_clean , by = "patent_id")

patents_2019 <- table2[!is.na(organization) & year == 2019 & type == 2, .N, by = organization][order(-N)]
patents_2019 %>% head(10)

#Question 3
table3 <- merge(x = pat_ass_merged , y = uspc_tbl , by = "patent_id") %>%
  unique()

patents_per_corp <- pat_ass_merged[!is.na(organization), .N, by = organization][order(-N)] 

table3_expanded <- merge(x = table3 , y = patents_per_corp , by = "organization")

min_patents <- patents_per_corp[10, N]

sector <- table3_expanded[N >= min_patents, .N , by = mainclass_id][order(-N)]
sector %>% head(5)

```
```{r Result}
library(readr)
library(data.table)
Question1 <- read_rds("DS_101/02_data_wrangling/Q1")
Question1
Question2 <- read_rds("DS_101/02_data_wrangling/Q2")
Question2
Question3 <- read_rds("DS_101/02_data_wrangling/Q3")
Question3
```
# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.